%-------------------------
% Resume in Latex
% Author : Brian Kam 
% Based off of: https://github.com/jakegut/resume
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubExpheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}



\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeActivitiesHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[1]{
    \item
    \begin{tabular*}{0.97\textwidth}{l}
      \small#1 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Brian Kam} \\ \vspace{1pt}
    \href{https://github.com/dhkam1102}{\underline{github.com/dhkam1102}}
    \href{https://linkedin.com/in/dhkam1102}{\underline{linkedin.com/in/dhkam1102}} $|$
    \href{mailto:brianhyunkam@gmail.com}{\underline{brianhyunkam@gmail.com}} $|$ 
    \href{location, STATE}{\underline{Los Angeles, CA}}

\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {UNIVERSITY OF CALIFORNIA IRVINE}{Irvine, CA}
      {Bachelor of Science in Computer Science, Dean’s List (4x)}{September 2020 -- March 2025}
      \resumeItem{Courses: Data Structures \& Algorithms, Project in Databases and Web Applications}
  \resumeSubHeadingListEnd



%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubExpheading
      {\textbf{EVEMETA} $-$ \emph{Software Engineer Intern}}{July 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Engineered and deployed Go-based microservices, enhancing system reliability by 10\% and reducing transaction errors by 10\% in a mid-scale IT environment, ensuring secure data transactions across business systems.}
        \resumeItem{Contributed to the development of a highly reliable video player as part of a team, focusing on implementing key features like play/pause, refresh, and advanced noise/haze reduction. These enhancements improved user satisfaction by 20\%, reduced buffering time by 25\%, and provided smooth, low-latency streaming at 60 FPS.}
        \resumeItem{Developed a system to aggregate news articles from multiple sources, reducing memory usage by 20\% through the use of NoSQL databases. Accelerated content delivery speed by 35\%, while boosting data availability and consistency.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Spotube Downloader} $|$ \emph{Python Project}}
          \resumeItemListStart
            \resumeItem{\textbf{Automated Playlist Conversion Solution}:  Designed a Python tool using youtube-dl, Spotify API, and web scraping techniques to automate playlist transfers from YouTube to Spotify. Reduced manual processing time by 85\% and improved media management efficiency.}
            \resumeItem{\textbf{Local Data Retention Solution}: Created a scalable data retention solution with SQLite and file compression, ensuring 100\% media retention and reducing storage costs by 40\%, enabling seamless access to media across platforms.}

            % \resumeItem{Local Data Retention Solution: Provides a scalable way to retain access to licensed media, ensuring data continuity. Ideal for individuals and organizations that require robust content management solutions in the digital media space.}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Fablix Movie Page} $|$ \emph{Java, Tomcat, AWS, GCP, Docker, Kubernetes}}
          \resumeItemListStart
            \resumeItem{\textbf{User Interface Development}: Crafted a responsive front-end using HTML, CSS, and JavaScript with advanced search, filtering, and autocomplete features for movies, optimizing the user experience for seamless navigation.}
            \resumeItem{\textbf{Back-End System Architecture}: Built a robust back-end in Java with Tomcat, using a master-slave MySQL database configuration to optimize query performance. Reduced query response time by 40\% and minimized user search errors by 18\% through efficient API endpoints and server-side logic.}
            \resumeItem{\textbf{Infrastructure optimization for large-scale deployment}: Managed the deployment and orchestration of the system using AWS load balancing, Kubernetes, and docker containers. Expaned scalability by 3x while reducing server response time by 30\%.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%

%-----------ACTIVITIES-----------
\section{Activities}
    \resumeSubHeadingListStart
      \resumeActivitiesHeading
          {\textbf{LikeLion} $|$ \emph{Co-founder of LikeLion UCI}}{August 2022 -- August 2023}
          \resumeItemListStart
            \resumeItem{\textbf{Led enterprise training initiatives}: Co-founded UCI’s first coding platform, facilitating peer learning for 100+ students with 80\% hands-on collaboration.}
            \resumeItem{\textbf{Directed coding and IT workshops}: Led 10+ workshops that trained participants in enterprise-level programming and IT practices, enhancing their ability to contribute to large-scale IT projects in Fortune 500 companies.}
            \resumeItem{\textbf{Established global IT network connections}: Connected with over 50+ students with LikeLion's global network, providing mentorship and collaboration in global IT initiatives, hackathons, and enterprise-level project developments. This resulted in 20\% of participants securing internship roles in tech}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Go, Java, C++, C, HTML/CSS, JavaScript} \\
     \textbf{Frameworks \& Library}{: Flask, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, GCP, Kubernetes, Tomcat, VS Code, Maven, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Concepts}{: Software Engineering, Data Structures and Algorithms, System Design, Cloud Infrastructure}\\
     \textbf{Language Proficiency}{: Fluent in English and Korean; Conversational Proficiency in Japanese}

    }}
 \end{itemize}


%-------------------------------------------
\end{document}
